Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-17 02_Paper/paper.tex
worked on section 2 and bib.bib

Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
This offers a wide range of applications. In the context of industrial or production enviroments, this includes for example 
predictive maintenance of machines, the increase of organization performance, production efficiency or improving product design %Quellen einfügen.
Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
etablished quality control methods, in terms of speed, accuracy and time delay.
%...

>>>>

Predictive analytics discover according to Delen and Damirkan explanatory and predictive patterns which represents 
the inherent relationships between data inputs and outputs, using data and mathematical techniques \cite{delen2013data}. 
This offers a wide range of applications. In the context of industrial or production enviroments, this includes in the areas of Processes, Products and Machines & Assets for example 
predictive maintenance, product design or optimization of routing and scheduling \cite{krauss2019machine}. 
Predictive analytics combined with quality control can be a powerful tool, because it is an improvement compared with the mentioned earlier currently
etablished quality control methods, in terms of speed, accuracy and time delay.
So far, only in exceptional cases in the literature is a combination of predictive analytics and quality control found \cite{aumi2012model, ritter1992neue}. With regard to general approaches to the use of predictive analytics,
for example in the form of machine learning in quality prediction, there is a lack in the literature. 
Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}. 
The few existing approaches are extended by this paper in that a demonstrator executes an industry-unspecific production/assembly process,
the collection and processing of the data from the process parameters in continous and a few different ML algorithms are used for prediction, 
in order to determine, which algorithms are most advantageous for predicting the quality of an outcoming product. 
In addition, it is described in detail how the collected data was collected, prepared and processed.
